--- 
title: "Stock Synthesis Vignettes"
author: "Elizabeth Gugliotti"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
color-links: yes
lot: yes
lof: yes
fontsize: 12 pt
site:  bookdown::bookdown_site
url: 'https://e-gugliotti-NOAA.github.io/test-vignettes/'
github-repo: e-gugliotti-NOAA/test-vignettes-bookdown
description: "This is an assemblage of vignettes to help Stock Synthesis users."
---

```{r setup, include=FALSE}
options(
  htmltools.dir.version = FALSE, formatR.indent = 2,
  width = 55, digits = 4, warnPartialMatchAttr = FALSE, warnPartialMatchDollar = FALSE
)
local({
  r = getOption('repos')
  if (!length(r) || identical(unname(r['CRAN']), '@CRAN@'))
    r['CRAN'] = 'https://cran.rstudio.com' 
  options(repos = r)
})
lapply(c('DT', 'formatR', 'svglite', 'rticles'), function(pkg) {
  if (system.file(package = pkg) == '') install.packages(pkg)
})
# install from github
githubs <- c('citr' = 'crsh/citr')
lapply(names(githubs), function(pkg) {
  if (system.file(package = pkg) == '') remotes::install_github(githubs[pkg], upgrade = FALSE)
})
```

# Prerequisites {-}


This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
